\plaintitle

### 2016-09-22 drafts/labor/piecework_lit.tex
piecework_lit

\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it;
  \item trace the rise of piecework at a very high level,
        identifying key figures and ideas during this time; and finally
  \item look at the fall of piecework, such as it was,
        considering in particular
        the factors that may have led to piecework's
        eventual demise in the American and European labor markets.
        % \msb{did it demise? there are sweatshops around the world today}.
        % \ali{is it okay to corner it off like this (by just being about the US/EU)?}
\end{inlinelist}
This section is not intended to be comprehensive: instead, it sets up the scaffolding necessary for our later investigations of crowd work's three questions: complexity limits, task decomposition, and worker relationships.

@@

\citeauthor{hughRaynbirdTaskWork} offers
a concise definition of piecework
--- which he variously also calls ``measure work'', ``grate work'', and ``task work'' ---
by contrasting the ``task--labourer'' with the ``day--labourer'':
``the chief difference lies between the day--labourer,
who receives a certain some of money\dots~for his day's work,
and the task--labourer, whose earnings depend on the \textit{quantity} of work done [emphasis added]''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} gives a more illustrative definition of piecework,
offering examples:
``payment is made for each hectare which is pronounced to be well ploughed~[\dots]~
for each living foal got from a mare;~[\dots]~
for each living calf got~[\dots]''~\cite{10.2307/2338394}.
This framing perhaps makes the most intuitive sense;
``payment for results'', as \citeauthor{10.2307/2338394} calls it,
is not only common in practice, but well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

Viewing crowd work as a modern instantiation of piecework is relatively straightforward by this definition. 
Platforms such as Mechanical Turk, Uber and TaskRabbit pay by the task, though some such as Upwork do offer hourly rates as well. 
% Second, workers on these platforms have significant freedom in choosing which tasks to work on, and when to log on and perform work~\cite{martin2014being,whyWouldAnyoneBrewer}. 
% Finally, computational workflows have successfully scaffolded many complex tasks into a series of small microtasks that can be performed without expertise.
%  \subsection{Piecework and crowd work}
% \msb{I assume this is forthcoming?}
% Using the definition of piecework that we came up with earlier, we argue that
% crowd work is fundamentally an instantiation of piecework, and
% that we can more precisely anticipate the answers to the open research questions we discussed earlier.
% We'll show that the dimensions of crowd work that the broader HCI community has been studying
% align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
% \subsection{From piecework to on--demand work}
% Crowd work and gig work are fundamentally an instantion of piecework.
% First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Finally, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.

Given this alignment, many of the same properties of piecework historically will apply to on--demand work as well. In the next section, we perform this application to three of the major questions in crowd work and gig work, identifying similarities and differences between historical piecework and modern on--demand work.

>>>>

\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{inlinelist}
  \item define ``piecework'' as researchers in the topic understood it; and
  \item trace the rise and fall of piecework at a very high level,
        identifying key figures and ideas during this time;
  %        and finally
  % \item look at the fall of piecework, such as it was,
  %       considering in particular
  %       the factors that may have led to piecework's
  %       eventual demise in the American and European labor markets.
        % \msb{did it demise? there are sweatshops around the world today}.
        % \ali{is it okay to corner it off like this (by just being about the US/EU)?}
\end{inlinelist}
This section is not intended to be comprehensive: instead, it sets up the scaffolding necessary for our later investigations of crowd work's three questions: complexity limits, task decomposition, and worker relationships.

@@

\citeauthor{hughRaynbirdTaskWork} offers
a concise definition of piecework
--- which he variously also calls ``measure work'', ``grate work'', and ``task work'' ---
by contrasting the ``task--labourer'' with the ``day--labourer'':
``the chief difference lies between the day--labourer,
who receives a certain some of money\dots~for his day's work,
and the task--labourer, whose earnings depend on the \textit{quantity} of work done [emphasis added]''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} gives a more illustrative definition of piecework,
offering examples:
``payment is made for each hectare which is pronounced to be well ploughed~[\dots]~
for each living foal got from a mare;~[\dots]~
for each living calf got''~\cite{10.2307/2338394}.
This framing perhaps makes the most intuitive sense;
``payment for results,'' as \citeauthor{10.2307/2338394} calls it,
is not only common in practice, but well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

Viewing crowd work as a modern instantiation of piecework is relatively straightforward by this definition. 
First, platforms such as Mechanical Turk, Uber and TaskRabbit pay by the task, though some such as Upwork do offer hourly rates as well. 
% Second, workers on these platforms have significant freedom in choosing which tasks to work on, and when to log on and perform work~\cite{martin2014being,whyWouldAnyoneBrewer}. 
% Finally, computational workflows have successfully scaffolded many complex tasks into a series of small microtasks that can be performed without expertise.
%  \subsection{Piecework and crowd work}
% \msb{I assume this is forthcoming?}
% Using the definition of piecework that we came up with earlier, we argue that
% crowd work is fundamentally an instantiation of piecework, and
% that we can more precisely anticipate the answers to the open research questions we discussed earlier.
% We'll show that the dimensions of crowd work that the broader HCI community has been studying
% align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
% \subsection{From piecework to on--demand work}
% Crowd work and gig work are fundamentally an instantion of piecework.
% First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Third, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.
Given this alignment, many of the same properties of piecework historically will apply to on--demand work as well. In the next section, we perform this application to three of the major questions in crowd work and gig work, identifying similarities and differences between historical piecework and modern on--demand work.
